Action letter

### 2021-05-10 manuscript.Rmd
Final submission

keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_pdf
knit              : worcs::cite_essential
header-includes:
  - \raggedbottom
---

@@

cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
vert$color <- cat_cols[vert$Category]
vert$shape <- cat_shapes[vert$Category]
vert$frame.color <- cat_cols[vert$Category]

@@

categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
if(any(!vert$name %in% categ$name)){
  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
  stop("Please re-categorize missing vertices.")
} 
vert$Category <- categ$category[match(vert$name, categ$name)]
vert$faded <- vert$name %in% df$cat[df$source == "theory"]
cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
vert$color <- cat_cols[vert$Category]
vert$shape <- cat_shapes[vert$Category]
vert$frame.color <- cat_cols[vert$Category]

@@

set.seed(4) #4 #2 #3
l1 <- l <- layout_with_fr(g1)
set.seed(3)
l2 <- layout_with_fr(g2)

p <- quote({
  # Set margins to 0
  par(mar=c(0.5,0.5,0.5,0.5),
      mfrow=c(1,2))
  plot(g1, edge.curved = 0, layout=l1,
       vertex.label.family = "sans",
       vertex.label.cex = 0.7,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
  plot(g2, edge.curved = 0, layout=l2,
       vertex.label.family = "sans",
       vertex.label.cex = 0.7,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "b")
})
saveRDS(g1, "bl_g1.RData")
saveRDS(g2, "bl_g2.RData")
saveRDS(l1, "bl_l1.RData")
saveRDS(l2, "bl_l2.RData")
# Save files

@@

@@

  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
  df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))

@@

  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
    geom_segment(aes(x = 0, xend = Frequency,
                     y = Word, yend = Word, linetype = notingraph), colour = "grey50"
    ) + 
    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"))+ #, guide = NULL
    scale_shape_manual(values = scale_shapes)+#, guide = NULL
    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
    scale_x_log10() +
    #scale_y_discrete(labels = italic_labels) +
    scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
    theme_bw() + theme(panel.grid.major.x = element_blank(),
                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                       legend.position = c(.70,.125),
                       legend.title = element_blank(),
                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))

@@

  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
  vert$color <- cat_cols[vert$Category]
  vert$shape <- cat_shapes[vert$Category]
  vert$frame.color <- cat_cols[vert$Category]
  vert$color[vert$faded] <- "#FFFFFF"

@@

  # Layout
  set.seed(6) #4
  l1 <- l <- layout_with_fr(g)
  l1[,1] <- -1*l1[,1]
  set.seed(64)
  l2 <- layout_in_circle(g, order = shifter(V(g), -3))

  p <- quote({
    # Set margins to 0
    par(mar=c(0,0,0,0),
        mfrow=c(1,2))
    plot(g, edge.curved = 0, layout=l1,
         vertex.label.family = "sans",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
    plot(g, edge.curved = 0, layout=l2,
         vertex.label.family = "sans",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
  })

@@

```{r message = FALSE, echo = FALSE, warning = FALSE, results="hide"}
p <- quote(cowplot::plot_grid(readRDS("s1_varimp.RData")+theme(legend.position = "none")+xlab("Word frequency (Analysis 1)"), readRDS("s2_varimp.RData")+xlab("Word frequency (Analysis 2)")))

png("varimps.png", height = 150, width = 200, units = "mm", res= 300)
eval(p)
dev.off()
```

@@

```{r}
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(yaml)
library(Rmpfr)
library(topicmodels)
library(udpipe)
library(slam)
library(tidytext)
library(ggplot2)
library(textrank)
source("word_functions.R")
source("circle2.R")

if(isTRUE(tools::md5sum("study2_df.RData") == "21abb2622dfd94d8bd3473ed56697f9e")){
  df <- readRDS("study2_df.RData")
} else {
  stop("Note: Study 2 file is out of date. Please run this code manually.")
  recs <- data.table(read.csv("recs_final.csv"))
  if(!is.data.table(recs)){
    browser()
  }
  recs[, "doc" := 1:nrow(recs)]

@@

# Exclude words
if(!run_everything){
  df_kw <- readRDS("study2_df_kw.RData")
} else {
  df_kw <- df[upos %in% c("NOUN", "ADJ"), ]
  df_kw <- df_kw[grepl("^[a-zA-Z].", df_kw$lemma), ]
  exclude_terms <- readLines("exclude_terms.txt")
  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df_kw$lemma)))
  df_kw <- df_kw[-exclude_these, ]
  saveRDS(df_kw, "study2_df_kw.RData")
}

@@

if(!run_everything){
  kw_tr <- readRDS("study2_textrank.RData")
} else {
  kw_tr <- textrank_keywords(x = df_kw$lemma[df_kw$upos %in% c("NOUN", "ADJ")], 
                             ngram_max = 3, sep = " ")
  saveRDS(kw_tr, "study2_textrank.RData")
}

if(!run_everything){
  df_analyze <- data.table(readRDS("study2_df_analyze.RData"))
} else {
  # Merge back with original data
  df_kw$keyword <- txt_recode_ngram(df_kw$lemma, compound = kw_tr$keywords$keyword, ngram = kw_tr$keywords$ngram, sep = " ")
  df_kw$keyword[!df_kw$keyword %in% kw_tr$keywords$keyword] <- NA

@@

  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
  geom_segment(aes(x = 0, xend = Frequency,
                   y = Word, yend = Word, linetype = notingraph), colour = "grey50"
  ) + 
  geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
  geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
  geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
  scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+#
  scale_shape_manual(values = scale_shapes, guide = NULL)+#
  scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL) +
  scale_x_log10() +
  #scale_y_discrete(labels = italic_labels) +
  scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
  guides(fill = guide_legend(title = NULL,
                               override.aes = list(linetype = c(1, 1, 1,1),
                                                   shape = scale_shapes,
                                                   colour = cat_cols[names(scale_shapes)]))) + 
theme_bw() + theme(panel.grid.major.x = element_blank(),
                   panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                   legend.position = c(.825,.1125),
                   legend.title = element_blank(),
                   axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
  saveRDS(p, "s2_varimp.RData")
  svg("s2_varimp.svg", width = 7/2.54, height = 14/2.54)
  eval(p)
  dev.off()

@@

  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
  vert$color <- cat_cols[vert$Category]
  vert$shape <- cat_shapes[vert$Category]
  vert$frame.color <- cat_cols[vert$Category]

@@

  p <- quote({
    # Set margins to 0
    par(mar=c(0,0,0,0),
        mfrow=c(1,2))
    plot(g, edge.curved = 0, layout=l1,
         vertex.label.family = "sans",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
    text(-1.1, y = -1, labels = "a")
    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)
    plot(g, edge.curved = 0, layout=l2,
         vertex.label.family = "sans",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
    text(-1.1, y = -1, labels = "b")
  })

@@

```
```{r mergenetworks}
cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
bl1 <- readRDS("bl_l1.RData")
bl2 <- readRDS("bl_l2.RData")
bg1 <- readRDS("bl_g1.RData")
bg2 <- readRDS("bl_g2.RData")
s1l <- readRDS("s1_l1.RData")
s2l <- readRDS("s2_l1.RData")
s1g <- readRDS("s1_g1.RData")
s2g <- readRDS("s2_g1.RData")
p <- quote({
  # Set margins to 0
  par(mar=c(0,0,0,0),
      mfrow=c(2,2))
  plot(bg1, edge.curved = 0,
       layout=bl1,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.7, bty="n", ncol=1)

  plot(bg2, edge.curved = 0,
       layout=bl2,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "b")
  plot(s1g, edge.curved = 0,
       layout=s1l,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "c")
  plot(s2g, edge.curved = 0,
       layout=s2l,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "d")
})

@@

p <- quote({
  # Set margins to 0
  par(mar=c(0.5,0.5,0.5,0.5),
      mfrow=c(1,2))
  plot(s1g, edge.curved = 0,
       layout=s1l,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       ##vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.4, cex=.6, bty="n", ncol=1)

  plot(s2g, edge.curved = 0,
       layout=s2l,
       vertex.label.family = "sans",
       vertex.label.cex = 0.5,
       ##vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  text(-1.1, y = -1, labels = "b")

@@

svg("tmnetworks.svg", width = 14)
eval(p)
dev.off()
```
The corpus for this second analysis consisted of the abstracts of the selected articles.
Keywords, as examined in Analysis 1, convey high-quality information because they are carefully chosen by authors to capture the essence of a study.
However, as authors are
typically limited to 5 keywords, some nuance may be lost.
Abstracts, by contrast, offer greater freedom of expression,
but present a greater challenge when it
comes to extracting relevant information.
It has been shown that retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
For example, nouns help capture terms like "emotion", and adjectives help capture the "mental" in "mental health".
The natural language processing technique "part-of-speech tagging" (POS-tagging) was used to identify each word's grammatical function within the sentence context.
Finally, stemming was used to reduce the retained terms to their root form;
a common procedure to ensure that terms are correctly classified regardless of their use in a sentence.
As in Analysis 1, heterogeneity was explored using latent dirichlet allocation - but no subcorpora were identified ([see online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)).

>>>>

keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_docx
knit              : worcs::cite_essential
header-includes:
  - \raggedbottom
---

@@

cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
vert$color <- cat_cols[vert$Category]
vert$shape <- cat_shapes[vert$Category]
vert$frame.color <- cat_cols[vert$Category]

@@

categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
if(any(!vert$name %in% categ$name)){
  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
  stop("Please re-categorize missing vertices.")
} 
vert$Category <- categ$category[match(vert$name, categ$name)]
vert$faded <- vert$name %in% df$cat[df$source == "theory"]
cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
vert$color <- cat_cols[vert$Category]
vert$shape <- cat_shapes[vert$Category]
vert$frame.color <- cat_cols[vert$Category]

@@

set.seed(4) #4 #2 #3
l1 <- l <- layout_with_fr(g1)
l1[1,] <- c(-2.21258774559817, 25.7)
l1[28, 2] <- 29.5
l1[6, 2] <- 30
l1[21, 1] <- -0.05

set.seed(3)
l2 <- layout_with_fr(g2)
l2[28, 2] <- -1.8
l2[5, 2] <- -4.5
l2[15, 2] <- -6.8

p <- quote({
  # Set margins to 0
  par(mar=c(0.5,0.5,0.5,0.5),
      mfrow=c(1,2))
  plot(g1, edge.curved = 0, layout=l1,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.7,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)
  plot(g2, edge.curved = 0, layout=l2,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.7,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "b")
})
saveRDS(g1, "bl_g1.RData")
saveRDS(g2, "bl_g2.RData")
saveRDS(l1, "bl_l1.RData")
saveRDS(l2, "bl_l2.RData")
# Save files

@@

loadfonts(device = "postscript") ## for postscript()
postscript("baseline_network.eps", height = (.5*7.9), width = 7.9,
           family = "Arial", paper = "special", onefile = FALSE,
           horizontal = FALSE)
eval(p)
dev.off()

@@

  cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
  df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))

@@

  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
    geom_segment(aes(x = 0, xend = Frequency,
                     y = Word, yend = Word, linetype = notingraph), colour = "grey50"
    ) + 
    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
    scale_colour_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"))+ #, guide = NULL
    scale_shape_manual(values = scale_shapes)+#, guide = NULL
    scale_fill_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")) +
    scale_x_log10() +
    #scale_y_discrete(labels = italic_labels) +
    scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
    theme_bw() + theme(panel.grid.major.x = element_blank(),
                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                       legend.position = c(.70,.125),
                       legend.title = element_blank(),
                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))

@@

  cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
  vert$color <- cat_cols[vert$Category]
  vert$shape <- cat_shapes[vert$Category]
  vert$frame.color <- cat_cols[vert$Category]
  vert$color[vert$faded] <- "#FFFFFF"

@@

  # Layout
  set.seed(6) #4
  l1 <- l <- layout_with_fr(g)
  l1[,1] <- -1*l1[,1]
  l1[23,2] <- 6.5
  l1[44,2] <- 6
  l1[6,2] <- 5.7
  l1[34,2] <- 5.3
  l1[26,] <- c(-1.8, 2.2)
  l1[5,1] <- -.4
  l1[40,1] <- -1.1
  l1[29,] <- c(-1,1.7)

  set.seed(64)
  l2 <- layout_in_circle(g, order = shifter(V(g), -3))

  p <- quote({
    # Set margins to 0
    par(mar=c(0,0,0,0),
        mfrow=c(1,2))
    plot(g, edge.curved = 0, layout=l1,
         vertex.label.family = "Arial",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
    )
    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.5, cex=.7, bty="n", ncol=1)
    plot(g, edge.curved = 0, layout=l2,
         vertex.label.family = "Arial",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
    )
  })

@@

```{r eval = TRUE, message = FALSE, echo = FALSE, warning = FALSE, results="hide"}
p <- quote(cowplot::plot_grid(readRDS("s1_varimp.RData")+theme(legend.position = "none")+xlab("Word frequency (Analysis 1)"), readRDS("s2_varimp.RData")+xlab("Word frequency (Analysis 2)")))

png("varimps.png", height = 150, width = 200, units = "mm", res= 300)
eval(p)
dev.off()
save_plot("varimps.eps", plot = eval(p), device = cairo_ps, base_height = ((150/200)*7.9), base_width = 7.9)
# loadfonts(device = "postscript") ## for postscript()
# postscript("varimps.eps", height = ((150/200)*7.9), width = 7.9,
#            family = "Arial", paper = "special", onefile = FALSE,
#            horizontal = FALSE)
# eval(p)
# dev.off()
```

@@

```{r}
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(yaml)
library(Rmpfr)
library(topicmodels)
library(udpipe)
library(slam)
library(tidytext)
library(ggplot2)
library(textrank)
source("word_functions.R")
source("circle2.R")
run_intensive = FALSE
if(!run_intensive){
  df <- readRDS("study2_df.RData")
} else {
  stop("Note: Study 2 file is out of date. Please run this code manually.")
  recs <- data.table(read.csv("recs_final.csv"))
  if(!is.data.table(recs)){
    browser()
  }
  recs[, "doc" := 1:nrow(recs)]

@@

# Exclude words
if(!run_intensive){
  df_kw <- readRDS("study2_df_kw.RData")
} else {
  df_kw <- df[upos %in% c("NOUN", "ADJ"), ]
  df_kw <- df_kw[grepl("^[a-zA-Z].", df_kw$lemma), ]
  exclude_terms <- readLines("exclude_terms.txt")
  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df_kw$lemma)))
  df_kw <- df_kw[-exclude_these, ]
  saveRDS(df_kw, "study2_df_kw.RData")
}

@@

if(!run_intensive){
  kw_tr <- readRDS("study2_textrank.RData")
} else {
  kw_tr <- textrank_keywords(x = df_kw$lemma[df_kw$upos %in% c("NOUN", "ADJ")], 
                             ngram_max = 3, sep = " ")
  saveRDS(kw_tr, "study2_textrank.RData")
}

if(!run_intensive){
  df_analyze <- data.table(readRDS("study2_df_analyze.RData"))
} else {
  # Merge back with original data
  df_kw$keyword <- txt_recode_ngram(df_kw$lemma, compound = kw_tr$keywords$keyword, ngram = kw_tr$keywords$ngram, sep = " ")
  df_kw$keyword[!df_kw$keyword %in% kw_tr$keywords$keyword] <- NA

@@

  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
  geom_segment(aes(x = 0, xend = Frequency,
                   y = Word, yend = Word, linetype = notingraph), colour = "grey50"
  ) + 
  geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
  geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat, shape = cat), fill = "white", size = 1.5) +
  geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat, shape = cat), size = 1.5) +
  scale_colour_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"), guide = NULL)+#
  scale_shape_manual(values = scale_shapes, guide = NULL)+#
  scale_fill_manual(values = c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4"), guide = NULL) +
  scale_x_log10() +
  #scale_y_discrete(labels = italic_labels) +
  scale_linetype_manual(values = c("TRUE" = 3, "FALSE" = 1), guide = NULL) +
  guides(fill = guide_legend(title = NULL,
                               override.aes = list(linetype = c(1, 1, 1,1),
                                                   shape = scale_shapes,
                                                   colour = cat_cols[names(scale_shapes)]))) + 
theme_bw() + theme(panel.grid.major.x = element_blank(),
                   panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                   legend.position = c(.81,.1125),
                   legend.title = element_blank(),
                   axis.text.y = element_text(hjust=0, vjust = 0, size = 6))
  saveRDS(p, "s2_varimp.RData")
  svg("s2_varimp.svg", width = 7/2.54, height = 14/2.54)
  eval(p)
  dev.off()

@@

  cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
  vert$color <- cat_cols[vert$Category]
  vert$shape <- cat_shapes[vert$Category]
  vert$frame.color <- cat_cols[vert$Category]

@@

  p <- quote({
    # Set margins to 0
    par(mar=c(0,0,0,0),
        mfrow=c(1,2))
    plot(g, edge.curved = 0, layout=l1,
         vertex.label.family = "Arial",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
    )
    text(-1.1, y = -1, labels = "a")
    legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col="#777777", pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)
    plot(g, edge.curved = 0, layout=l2,
         vertex.label.family = "Arial",
         vertex.label.cex = 0.5,
         #vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
    )
    text(-1.1, y = -1, labels = "b")
  })

@@

```
```{r mergenetworks}
cat_cols <- c(Outcome = "gray55", Indicator = "tomato", Cause = "darkgoldenrod3", Protective = "olivedrab4")
bl1 <- readRDS("bl_l1.RData")
bl2 <- readRDS("bl_l2.RData")
bg1 <- readRDS("bl_g1.RData")
bg2 <- readRDS("bl_g2.RData")
s1l <- readRDS("s1_l1.RData")
s1l[23,2] <- 6.5
s1l[44,2] <- 6
s1l[6,2] <- 5.7
s1l[34,2] <- 5.3
s1l[26,] <- c(-1.8, 2.2)
s1l[5,1] <- -.4
s1l[40,1] <- -1.1
s1l[29,] <- c(-1,1.7)
s2l <- readRDS("s2_l1.RData")
s1g <- readRDS("s1_g1.RData")
s2g <- readRDS("s2_g1.RData")
p <- quote({
  # Set margins to 0
  par(mar=c(0,0,0,0),
      mfrow=c(2,2))
  plot(bg1, edge.curved = 0,
       layout=bl1,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.1, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.7, bty="n", ncol=1)

  plot(bg2, edge.curved = 0,
       layout=bl2,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "b")
  plot(s1g, edge.curved = 0,
       layout=s1l,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "c")
  plot(s2g, edge.curved = 0,
       layout=s2l,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       #vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "d")
})

@@

p <- quote({
  # Set margins to 0
  par(mar=c(0.5,0.5,0.5,0.5),
      mfrow=c(1,2))
  plot(s1g, edge.curved = 0,
       layout=s1l,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       ##vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "a")
  legend(x=-1.2, y=1.1, names(cat_cols), pch=legend_shapes, col=cat_cols, pt.bg=cat_cols, pt.cex=1.2, cex=.6, bty="n", ncol=1)

  plot(s2g, edge.curved = 0,
       layout=s2l,
       vertex.label.family = "Arial",
       vertex.label.cex = 0.5,
       ##vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2,
         edge.color = "gray70" # edge.color = rgb(0,0,0,.2)
  )
  text(-1.1, y = -1, labels = "b")

@@

svg("tmnetworks.svg", width = 14)
eval(p)
dev.off()

loadfonts(device = "postscript") ## for postscript()
postscript("tmnetworks.eps", height = (.5*7.9), width = 7.9,
           family = "Arial", paper = "special", onefile = FALSE,
           horizontal = FALSE)
eval(p)
dev.off()
```
The corpus for this second analysis consisted of the abstracts of the selected articles.
Keywords, as examined in Analysis 1, convey high-quality information because they are carefully chosen by authors to capture the essence of a study.
However, as authors are
typically limited to 5 keywords, some nuance may be lost.
Abstracts, by contrast, offer greater freedom of expression,
but present a greater challenge when it
comes to extracting relevant information.
It has been shown that retaining nouns and adjectives generally helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
For example, nouns help capture terms like "emotion", and adjectives help capture the "mental" in "mental health".
The natural language processing technique "part-of-speech tagging" (POS-tagging) was used to identify each word's grammatical function within the sentence context.
Finally, stemming was used to reduce the retained terms to their root form;
a common procedure to ensure that terms are correctly classified regardless of their use in a sentence.
As in Analysis 1, heterogeneity was explored using latent dirichlet allocation - but no subcorpora were identified ([see online supplement](https://github.com/cjvanlissa/veni_sysrev/blob/master/topic_models.md)).
